Research Journal

### 2018-09-18 journal/main.tex
Added a bunch of experiments to journal entry

%% Useful packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage[caption=false]{subfig} % subfigures.  false option prevents conflicts in caption styling with other packages
\usepackage{float}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

@@

>>>>

%% Useful packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage[caption=false]{subfig} % subfigures.  false option prevents conflicts in caption styling with other packages
\usepackage{multirow}
\usepackage{multirow}
\usepackage{float}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

@@

\entry{2018}{07}{09}
\subsection*{TensorFlow Implementation Details}
Still working on updating the TensorFlow features to use Sonnet.

\entry{2018}{09}{17}
I have much ground to catch up on. But better late than never.
\subsection*{TensorFlow Implementation Details Completed}
I finished this and the code is much cleaner - the code is divided better. The \texttt{model.py} function has been replaced with a model module (directory with multiple files), so now custom layers, custom network types, and the architecture selection logic are separated. However, the regularization is still a bit crude, and when building a new architecture it tends to give a 'gotcha' - I need to fix that. Otherwise it is working much better.
\subsection*{Binary Cross Entropy afterthoughts}
I have not tested this extensively but the limited experiments I did try didn't seem to make much of a difference. I think it might be better dealing with outliers. Right now we use a Frobenious norm loss, which implicitly assumes $A_{ij} \sim \mathcal{N}(e_i^\top e_j, \sigma^2)$. This assumes infinte support and is not quite we are assuming if we enforce $e_i$ to be norm 1. Thus the rational is since it is between 0 and 1, we can treat each element as a classifcation: $P(A_{ij} = 1) = 1 - P(A_{ij} = 0) = e_i^\top e_j$. This is more appropriate and possibly more robust to noise (maybe outliers?). However, more tests need to be done to determine its actual effectiveness.
\subsection*{Experiments}
Many experiments were done during this time. Here are the tables and figures

\subsubsection*{Experiment Run 12}
Dataset type $\texttt{synth3view}$ - noiseless 3 view dataset.

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/synth-3view-skip-relu-unsup-false-0}
  \label{fig:synth-3view-skip-relu-unsup-false-0-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for best performing of this set}
\end{figure}
\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/synth-3view-skip-leakyrelu-unsup-true-0}
  \label{fig:synth-3view-skip-leakyrelu-unsup-true-0-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for worst performing of this set}
\end{figure}
\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/synth-3view-skip-relu-unsup-true-0}
  \label{fig:synth-3view-skip-relu-unsup-true-0-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for random experiment of this set}
\end{figure}
\begin{table}[H]
  \caption{Numerical results}
      \begin{tabular}{|c|c|c|c|} \hline
                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
Baseline   & 5.11e-01 $\pm$ 3.90e-01 & 2.56e-01 $\pm$ 2.06e-01 \\ \hline
Skip Type 0 Arch., LeakyReLU, Supervised   & 9.92e-01 $\pm$ 1.68e-02 & 1.10e-01 $\pm$ 1.32e-01 \\ \hline
Skip Type 0 Arch., LeakyReLU, Unsupervised   & 9.97e-01 $\pm$ 6.13e-03 & 1.25e-01 $\pm$ 1.31e-01 \\ \hline
Skip Type 0 Arch., ReLU, Supervised   & 9.98e-01 $\pm$ 4.96e-03 & 9.04e-02 $\pm$ 1.37e-01 \\ \hline
Skip Type 0 Arch., ReLU, Unsupervised   & 9.98e-01 $\pm$ 5.27e-03 & 1.19e-01 $\pm$ 1.30e-01 \\ \hline
Skip Type 1 Arch., LeakyReLU, Supervised   & 9.97e-01 $\pm$ 7.39e-03 & 9.74e-02 $\pm$ 1.38e-01 \\ \hline
Skip Type 1 Arch., LeakyReLU, Unsupervised   & 9.94e-01 $\pm$ 1.04e-02 & 1.21e-01 $\pm$ 1.31e-01 \\ \hline
Skip Type 1 Arch., ReLU, Supervised   & 9.98e-01 $\pm$ 5.89e-03 & 8.48e-02 $\pm$ 1.41e-01 \\ \hline
Skip Type 1 Arch., ReLU, Unsupervised   & 9.96e-01 $\pm$ 7.70e-03 & 1.16e-01 $\pm$ 1.32e-01 \\ \hline
      \end{tabular}
      \label{fig:12_tab1}
\end{table}

\subsubsection*{Experiment Run 13}
Using ReLU activation type with aforementioned pairwise noise. 
The ``Long Skip'' type architecture is basically the skip type but with additional skip connections from layer 1 to layer $n/2$ and layer $n$.
This helps training and performance a fair amount since it allows way more layers (doubling or tripling).

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/pairwise5-skip0-relu-ld-false-unsup-true-0}
  \label{fig:pairwise5-skip0-relu-ld-false-unsup-true-0-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for best performing of this set}
\end{figure}
\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/pairwise3-attn2-relu-ld-true-unsup-false-0}
  \label{fig:pairwise3-attn2-relu-ld-true-unsup-false-0-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for worst performing of this set}
\end{figure}
\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/pairwise3-longskip0-relu-ld-true-unsup-false-0}
  \label{fig:pairwise3-longskip0-relu-ld-true-unsup-false-0-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for random experiment of this set}
\end{figure}

\begin{table}[H]
  \caption{\texttt{pairwise3} results}
      \begin{tabular}{|l|c|c|c|} \hline
                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
Baseline   & 5.11e-01 $\pm$ 3.90e-01 & 2.56e-01 $\pm$ 2.06e-01 \\ \hline
\multicolumn{3}{|c|}{Data type \texttt{pairwise3} with generated data} \\ \hline
GAT Network Type 0 Arch., Supervised   & 5.75e-01 $\pm$ 3.58e-01 & 2.26e-01 $\pm$ 1.77e-01 \\ \hline
GAT Network Type 0 Arch., Unsupervised   & 7.11e-01 $\pm$ 2.65e-01 & 1.74e-01 $\pm$ 1.41e-01 \\ \hline
GAT Network Type 1 Arch., Supervised   & 5.96e-01 $\pm$ 3.44e-01 & 2.07e-01 $\pm$ 1.65e-01 \\ \hline
GAT Network Type 1 Arch., Unsupervised   & 7.65e-01 $\pm$ 2.36e-01 & 1.87e-01 $\pm$ 1.53e-01 \\ \hline
GAT Network Type 2 Arch., Supervised   & 8.33e-01 $\pm$ 1.79e-01 & 2.17e-01 $\pm$ 1.67e-01 \\ \hline
GAT Network Type 2 Arch., Unsupervised   & 5.13e-01 $\pm$ 3.89e-01 & 1.98e-01 $\pm$ 1.71e-01 \\ \hline
Long Skip Type 0 Arch., Supervised   & 9.90e-01 $\pm$ 2.35e-02 & 7.18e-02 $\pm$ 1.60e-01 \\ \hline
Long Skip Type 0 Arch., Unsupervised   & 9.59e-01 $\pm$ 6.03e-02 & 1.00e-01 $\pm$ 1.57e-01 \\ \hline
Skip Connections Type 1 Arch., Supervised   & 9.74e-01 $\pm$ 5.64e-02 & 9.52e-02 $\pm$ 1.60e-01 \\ \hline
Skip Connections Type 1 Arch., Unsupervised   & 9.66e-01 $\pm$ 7.82e-02 & 8.26e-02 $\pm$ 1.61e-01 \\ \hline
\multicolumn{3}{|c|}{Data type \texttt{pairwise3} with prestored data} \\ \hline
GAT Network Type 0 Arch., Supervised   & 5.95e-01 $\pm$ 3.45e-01 & 2.05e-01 $\pm$ 1.66e-01 \\ \hline
GAT Network Type 0 Arch., Unsupervised   & 6.64e-01 $\pm$ 3.15e-01 & 1.82e-01 $\pm$ 1.68e-01 \\ \hline
GAT Network Type 1 Arch., Supervised   & 5.09e-01 $\pm$ 3.93e-01 & 2.21e-01 $\pm$ 1.87e-01 \\ \hline
GAT Network Type 1 Arch., Unsupervised   & 7.07e-01 $\pm$ 2.76e-01 & 1.64e-01 $\pm$ 1.47e-01 \\ \hline
GAT Network Type 2 Arch., Supervised   & 4.92e-01 $\pm$ 4.00e-01 & 2.30e-01 $\pm$ 1.98e-01 \\ \hline
GAT Network Type 2 Arch., Unsupervised   & 6.12e-01 $\pm$ 3.33e-01 & 2.04e-01 $\pm$ 1.65e-01 \\ \hline
Long Skip Type 0 Arch., Supervised   & 9.80e-01 $\pm$ 3.75e-02 & 8.56e-02 $\pm$ 1.57e-01 \\ \hline
Long Skip Type 0 Arch., Unsupervised   & 9.62e-01 $\pm$ 5.32e-02 & 1.01e-01 $\pm$ 1.61e-01 \\ \hline
Skip Connections Type 1 Arch., Supervised   & 9.73e-01 $\pm$ 6.48e-02 & 8.12e-02 $\pm$ 1.60e-01 \\ \hline
Skip Connections Type 1 Arch., Unsupervised   & 9.66e-01 $\pm$ 7.71e-02 & 8.23e-02 $\pm$ 1.57e-01 \\ \hline
      \end{tabular}
      \label{fig:13_tab1}
\end{table}

\begin{table}[H]
  \caption{\texttt{pairwise5} results}
      \begin{tabular}{|l|c|c|c|} \hline
                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
Baseline   & 5.11e-01 $\pm$ 3.90e-01 & 2.56e-01 $\pm$ 2.06e-01 \\ \hline
\multicolumn{3}{|c|}{Data type \texttt{pairwise5} with generated data} \\ \hline
GAT Network Type 0 Arch., Supervised   & 5.04e-01 $\pm$ 3.97e-01 & 2.12e-01 $\pm$ 1.90e-01 \\ \hline
GAT Network Type 0 Arch., Unsupervised   & 7.51e-01 $\pm$ 2.39e-01 & 2.06e-01 $\pm$ 1.57e-01 \\ \hline
GAT Network Type 1 Arch., Supervised   & 6.99e-01 $\pm$ 2.74e-01 & 1.99e-01 $\pm$ 1.53e-01 \\ \hline
GAT Network Type 1 Arch., Unsupervised   & 5.41e-01 $\pm$ 3.74e-01 & 2.16e-01 $\pm$ 1.79e-01 \\ \hline
GAT Network Type 2 Arch., Supervised   & 6.72e-01 $\pm$ 2.90e-01 & 2.01e-01 $\pm$ 1.55e-01 \\ \hline
GAT Network Type 2 Arch., Unsupervised   & 5.09e-01 $\pm$ 3.93e-01 & 1.94e-01 $\pm$ 1.83e-01 \\ \hline
Long Skip Type 0 Arch., Supervised   & 9.68e-01 $\pm$ 5.29e-02 & 9.50e-02 $\pm$ 1.58e-01 \\ \hline
Long Skip Type 0 Arch., Unsupervised   & 9.40e-01 $\pm$ 7.90e-02 & 1.11e-01 $\pm$ 1.54e-01 \\ \hline
Skip Connections Type 1 Arch., Supervised   & 9.69e-01 $\pm$ 7.55e-02 & 6.14e-02 $\pm$ 1.43e-01 \\ \hline
Skip Connections Type 1 Arch., Unsupervised   & 9.66e-01 $\pm$ 8.32e-02 & 6.17e-02 $\pm$ 1.37e-01 \\ \hline
\multicolumn{3}{|c|}{Data type \texttt{pairwise5} with prestored data} \\ \hline
GAT Network Type 0 Arch., Supervised   & 8.06e-01 $\pm$ 2.14e-01 & 1.88e-01 $\pm$ 1.63e-01 \\ \hline
GAT Network Type 0 Arch., Unsupervised   & 5.92e-01 $\pm$ 3.56e-01 & 1.76e-01 $\pm$ 1.71e-01 \\ \hline
GAT Network Type 1 Arch., Supervised   & 4.96e-01 $\pm$ 3.99e-01 & 2.27e-01 $\pm$ 1.97e-01 \\ \hline
GAT Network Type 1 Arch., Unsupervised   & 5.95e-01 $\pm$ 3.44e-01 & 2.06e-01 $\pm$ 1.65e-01 \\ \hline
GAT Network Type 2 Arch., Supervised   & 8.11e-01 $\pm$ 2.06e-01 & 2.02e-01 $\pm$ 1.68e-01 \\ \hline
GAT Network Type 2 Arch., Unsupervised   & 5.84e-01 $\pm$ 3.49e-01 & 1.96e-01 $\pm$ 1.62e-01 \\ \hline
Long Skip Type 0 Arch., Supervised   & 9.66e-01 $\pm$ 5.37e-02 & 9.77e-02 $\pm$ 1.60e-01 \\ \hline
Long Skip Type 0 Arch., Unsupervised   & 9.74e-01 $\pm$ 4.28e-02 & 8.56e-02 $\pm$ 1.51e-01 \\ \hline
Skip Connections Type 1 Arch., Supervised   & 9.69e-01 $\pm$ 7.68e-02 & 6.22e-02 $\pm$ 1.44e-01 \\ \hline
Skip Connections Type 1 Arch., Unsupervised   & 9.65e-01 $\pm$ 8.34e-02 & 6.49e-02 $\pm$ 1.42e-01 \\ \hline
      \end{tabular}
      \label{fig:13_tab2}
\end{table}

\subsubsection*{Experiment Run 14}
Comparison between GAT and Sparse GAT architecture

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/pairwise3-spattn0-0-0}
  \label{fig:pairwise3-spattn0-0-0-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for best performing of this set}
\end{figure}
\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/pairwise5-attn0-0-0}
  \label{fig:pairwise5-attn0-0-0-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for worst performing of this set}
\end{figure}
\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/pairwise3-spattn1-0-1}
  \label{fig:pairwise3-spattn1-0-1-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for random experiment of this se}
\end{figure}
\begin{table}[H]
  \caption{Numerical results}
      \begin{tabular}{|c|c|c|c|} \hline
                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
Baseline   & 5.12e-01 $\pm$ 3.91e-01 & 2.56e-01 $\pm$ 2.06e-01 \\ \hline
\multicolumn{3}{|c|}{Data type \texttt{pairwise3} with prestored data} \\ \hline
GAT Network Type 0 Architecture   & 7.38e-01 $\pm$ 2.60e-01 & 1.52e-01 $\pm$ 1.55e-01 \\ \hline
GAT Network Type 0 Architecture   & 7.38e-01 $\pm$ 2.60e-01 & 1.52e-01 $\pm$ 1.55e-01 \\ \hline
GAT Network Type 1 Architecture   & 7.19e-01 $\pm$ 2.62e-01 & 1.87e-01 $\pm$ 1.64e-01 \\ \hline
GAT Network Type 1 Architecture   & 7.19e-01 $\pm$ 2.62e-01 & 1.87e-01 $\pm$ 1.64e-01 \\ \hline
Sparse GAT Network Type 0 Architecture   & 8.90e-01 $\pm$ 1.36e-01 & 1.68e-01 $\pm$ 1.61e-01 \\ \hline
Sparse GAT Network Type 0 Architecture   & 8.90e-01 $\pm$ 1.36e-01 & 1.68e-01 $\pm$ 1.61e-01 \\ \hline
Sparse GAT Network Type 1 Architecture   & 9.80e-01 $\pm$ 5.07e-02 & 8.68e-02 $\pm$ 1.43e-01 \\ \hline
Sparse GAT Network Type 1 Architecture   & 9.80e-01 $\pm$ 5.07e-02 & 8.68e-02 $\pm$ 1.43e-01 \\ \hline
\multicolumn{3}{|c|}{Data type \texttt{pairwise5} with prestored data} \\ \hline
GAT Network Type 0 Architecture   & 6.83e-01 $\pm$ 3.22e-01 & 4.33e-01 $\pm$ 2.63e-01 \\ \hline
GAT Network Type 0 Architecture   & 6.83e-01 $\pm$ 3.22e-01 & 4.33e-01 $\pm$ 2.63e-01 \\ \hline
GAT Network Type 1 Architecture   & 6.36e-01 $\pm$ 3.54e-01 & 1.97e-01 $\pm$ 2.00e-01 \\ \hline
GAT Network Type 1 Architecture   & 6.36e-01 $\pm$ 3.54e-01 & 1.97e-01 $\pm$ 2.00e-01 \\ \hline
Sparse GAT Network Type 0 Architecture   & 9.50e-01 $\pm$ 8.77e-02 & 1.16e-01 $\pm$ 1.49e-01 \\ \hline
Sparse GAT Network Type 0 Architecture   & 9.50e-01 $\pm$ 8.77e-02 & 1.16e-01 $\pm$ 1.49e-01 \\ \hline
Sparse GAT Network Type 1 Architecture   & 6.24e-01 $\pm$ 3.50e-01 & 3.99e-01 $\pm$ 2.62e-01 \\ \hline
Sparse GAT Network Type 1 Architecture   & 6.24e-01 $\pm$ 3.50e-01 & 3.99e-01 $\pm$ 2.62e-01 \\ \hline
\multicolumn{3}{|c|}{Data type \texttt{pairwise5} with data generation} \\ \hline
GAT Network Type 0 Architecture   & 5.26e-01 $\pm$ 3.87e-01 & 2.31e-01 $\pm$ 1.94e-01 \\ \hline
GAT Network Type 0 Architecture   & 5.26e-01 $\pm$ 3.87e-01 & 2.31e-01 $\pm$ 1.94e-01 \\ \hline
GAT Network Type 0 Architecture   & 4.87e-01 $\pm$ 4.07e-01 & 2.13e-01 $\pm$ 2.00e-01 \\ \hline
GAT Network Type 0 Architecture   & 4.87e-01 $\pm$ 4.07e-01 & 2.13e-01 $\pm$ 2.00e-01 \\ \hline
GAT Network Type 0 Architecture   & 4.88e-01 $\pm$ 4.06e-01 & 2.17e-01 $\pm$ 1.97e-01 \\ \hline
GAT Network Type 0 Architecture   & 4.88e-01 $\pm$ 4.06e-01 & 2.17e-01 $\pm$ 1.97e-01 \\ \hline
GAT Network Type 0 Architecture   & 4.87e-01 $\pm$ 4.02e-01 & 2.23e-01 $\pm$ 1.98e-01 \\ \hline
GAT Network Type 0 Architecture   & 4.87e-01 $\pm$ 4.02e-01 & 2.23e-01 $\pm$ 1.98e-01 \\ \hline
Sparse GAT Network Type 0 Architecture   & 9.30e-01 $\pm$ 1.36e-01 & 1.42e-01 $\pm$ 1.53e-01 \\ \hline
Sparse GAT Network Type 0 Architecture   & 9.30e-01 $\pm$ 1.36e-01 & 1.42e-01 $\pm$ 1.53e-01 \\ \hline
Sparse GAT Network Type 0 Architecture   & 9.31e-01 $\pm$ 1.23e-01 & 1.33e-01 $\pm$ 1.56e-01 \\ \hline
Sparse GAT Network Type 0 Architecture   & 9.31e-01 $\pm$ 1.23e-01 & 1.33e-01 $\pm$ 1.56e-01 \\ \hline
Sparse GAT Network Type 0 Architecture   & 8.81e-01 $\pm$ 1.57e-01 & 1.51e-01 $\pm$ 1.48e-01 \\ \hline
Sparse GAT Network Type 0 Architecture   & 8.81e-01 $\pm$ 1.57e-01 & 1.51e-01 $\pm$ 1.48e-01 \\ \hline
Sparse GAT Network Type 0 Architecture   & 9.30e-01 $\pm$ 1.17e-01 & 1.38e-01 $\pm$ 1.57e-01 \\ \hline
Sparse GAT Network Type 0 Architecture   & 9.30e-01 $\pm$ 1.17e-01 & 1.38e-01 $\pm$ 1.57e-01 \\ \hline
      \end{tabular}
      \label{fig:{0}_tab1}
\end{table}

\subsubsection*{Experiment Run 16}
(Run 16 had some errors)
Testing on outliers. An outlier is the following noise model:
\begin{equation*}
Hi
\end{equation*}
All the architectures are of type Long Skip Type 0 Arch. (\texttt{longskip0}).

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/outlier1-longskip0-load-false-1}
  \label{fig:outlier1-longskip0-load-false-1-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for best performing of this set}
\end{figure}
\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/outlier8-longskip0-load-false-0}
  \label{fig:outlier8-longskip0-load-false-0-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for worst performing of this set}
\end{figure}
\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/outlier2-longskip0-load-false-1}
  \label{fig:outlier2-longskip0-load-false-1-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for random experiment of this set}
\end{figure}

\begin{table}[H]
  \caption{Numerical results}
      \begin{tabular}{|l|c|c|c|} \hline
                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
Baseline   & 5.10e-01 $\pm$ 3.90e-01 & 2.56e-01 $\pm$ 2.06e-01 \\ \hline
Data type \texttt{outlier1} & 9.73e-01 $\pm$ 9.43e-02 & 1.53e-01 $\pm$ 1.39e-01 \\ \hline
Data type \texttt{outlier1} & 9.75e-01 $\pm$ 7.25e-02 & 1.51e-01 $\pm$ 1.44e-01 \\ \hline
Data type \texttt{outlier1} & 9.70e-01 $\pm$ 9.98e-02 & 1.53e-01 $\pm$ 1.40e-01 \\ \hline
Data type \texttt{outlier2} & 9.28e-01 $\pm$ 1.51e-01 & 1.57e-01 $\pm$ 1.39e-01 \\ \hline
Data type \texttt{outlier2} & 9.38e-01 $\pm$ 1.43e-01 & 1.60e-01 $\pm$ 1.38e-01 \\ \hline
Data type \texttt{outlier2} & 9.46e-01 $\pm$ 1.32e-01 & 1.50e-01 $\pm$ 1.36e-01 \\ \hline
Data type \texttt{outlier4} & 9.33e-01 $\pm$ 1.79e-01 & 1.46e-01 $\pm$ 1.50e-01 \\ \hline
Data type \texttt{outlier4} & 9.17e-01 $\pm$ 1.74e-01 & 1.58e-01 $\pm$ 1.41e-01 \\ \hline
Data type \texttt{outlier4} & 9.29e-01 $\pm$ 1.79e-01 & 1.41e-01 $\pm$ 1.48e-01 \\ \hline
Data type \texttt{outlier8} & 8.99e-01 $\pm$ 1.95e-01 & 1.61e-01 $\pm$ 1.40e-01 \\ \hline
Data type \texttt{outlier8} & 9.27e-01 $\pm$ 1.79e-01 & 1.40e-01 $\pm$ 1.51e-01 \\ \hline
Data type \texttt{outlier8} & 9.22e-01 $\pm$ 1.97e-01 & 1.35e-01 $\pm$ 1.53e-01 \\ \hline
      \end{tabular}
      \label{fig:tab1}
\end{table}

\subsubsection*{Experiment Run 17}
This was experimenting to see if we could handle more views. As the Long Skip type architectures seemed to work better.

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/pairwise5view5-longskip0-load-true-1}
  \label{fig:pairwise5view5-longskip0-load-true-1-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for best performing of this set}
\end{figure}
\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/6view-longskip0-load-true-0}
  \label{fig:6view-longskip0-load-true-0-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for worst performing of this set}
\end{figure}
\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/pairwise3view5-longskip1-load-true-1}
  \label{fig:pairwise3view5-longskip1-load-true-1-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for random experiment of this set}
\end{figure}

\begin{table}[H]
  \caption{Numerical results}
      \begin{tabular}{|l|c|c|c|} \hline
                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
Baseline   & 4.14e-01 $\pm$ 3.54e-01 & 2.61e-01 $\pm$ 2.13e-01 \\ \hline
\multicolumn{3}{|c|}{Data type \texttt{4view} with prestored data} \\ \hline
Long Skip Type 0 Arch.   & 9.47e-01 $\pm$ 8.19e-02 & 1.61e-01 $\pm$ 1.41e-01 \\ \hline
Long Skip Type 0 Arch.   & 1.00e+00 $\pm$ 1.14e-03 & 1.53e-01 $\pm$ 1.37e-01 \\ \hline
Long Skip Type 0 Arch.   & 9.06e-01 $\pm$ 1.32e-01 & 1.59e-01 $\pm$ 1.53e-01 \\ \hline
Long Skip Type 1 Arch.   & 1.00e+00 $\pm$ 2.75e-04 & 1.24e-01 $\pm$ 1.72e-01 \\ \hline
Long Skip Type 1 Arch.   & 1.00e+00 $\pm$ 6.56e-04 & 1.17e-01 $\pm$ 1.72e-01 \\ \hline
Long Skip Type 1 Arch.   & 9.99e-01 $\pm$ 4.87e-03 & 1.51e-01 $\pm$ 1.38e-01 \\ \hline
\multicolumn{3}{|c|}{Data type \texttt{5view} with prestored data} \\ \hline
Long Skip Type 0 Arch.   & 8.96e-01 $\pm$ 1.33e-01 & 1.66e-01 $\pm$ 1.62e-01 \\ \hline
Long Skip Type 0 Arch.   & 9.99e-01 $\pm$ 2.73e-03 & 1.50e-01 $\pm$ 1.37e-01 \\ \hline
Long Skip Type 0 Arch.   & 1.00e+00 $\pm$ 1.30e-03 & 1.50e-01 $\pm$ 1.35e-01 \\ \hline
Long Skip Type 1 Arch.   & 1.00e+00 $\pm$ 4.15e-04 & 1.22e-01 $\pm$ 1.67e-01 \\ \hline
Long Skip Type 1 Arch.   & 9.99e-01 $\pm$ 2.63e-03 & 1.52e-01 $\pm$ 1.44e-01 \\ \hline
Long Skip Type 1 Arch.   & 9.99e-01 $\pm$ 2.98e-03 & 1.50e-01 $\pm$ 1.43e-01 \\ \hline
\multicolumn{3}{|c|}{Data type \texttt{6view} with prestored data} \\ \hline
Long Skip Type 0 Arch.   & 8.48e-01 $\pm$ 1.75e-01 & 1.98e-01 $\pm$ 1.72e-01 \\ \hline
Long Skip Type 0 Arch.   & 9.98e-01 $\pm$ 5.64e-03 & 1.48e-01 $\pm$ 1.42e-01 \\ \hline
Long Skip Type 0 Arch.   & 9.99e-01 $\pm$ 3.27e-03 & 1.50e-01 $\pm$ 1.36e-01 \\ \hline
Long Skip Type 1 Arch.   & 9.99e-01 $\pm$ 1.93e-03 & 1.47e-01 $\pm$ 1.39e-01 \\ \hline
Long Skip Type 1 Arch.   & 1.00e+00 $\pm$ 6.77e-04 & 1.26e-01 $\pm$ 1.82e-01 \\ \hline
Long Skip Type 1 Arch.   & 1.00e+00 $\pm$ 1.76e-03 & 1.24e-01 $\pm$ 1.75e-01 \\ \hline
\multicolumn{3}{|c|}{Data type \texttt{pairwise3view5} with prestored data} \\ \hline
Long Skip Type 0 Arch.   & 9.86e-01 $\pm$ 2.63e-02 & 9.36e-02 $\pm$ 1.57e-01 \\ \hline
Long Skip Type 0 Arch.   & 9.79e-01 $\pm$ 3.44e-02 & 1.06e-01 $\pm$ 1.64e-01 \\ \hline
Long Skip Type 1 Arch.   & 9.80e-01 $\pm$ 2.63e-02 & 1.14e-01 $\pm$ 1.60e-01 \\ \hline
Long Skip Type 1 Arch.   & 9.89e-01 $\pm$ 2.47e-02 & 7.67e-02 $\pm$ 1.56e-01 \\ \hline
\multicolumn{3}{|c|}{Data type \texttt{pairwise3view6} with prestored data} \\ \hline
Long Skip Type 0 Arch.   & 8.98e-01 $\pm$ 9.67e-02 & 1.51e-01 $\pm$ 1.51e-01 \\ \hline
Long Skip Type 0 Arch.   & 9.84e-01 $\pm$ 3.16e-02 & 7.46e-02 $\pm$ 1.57e-01 \\ \hline
Long Skip Type 1 Arch.   & 8.37e-01 $\pm$ 1.51e-01 & 1.47e-01 $\pm$ 1.61e-01 \\ \hline
Long Skip Type 1 Arch.   & 8.39e-01 $\pm$ 1.63e-01 & 1.37e-01 $\pm$ 1.51e-01 \\ \hline
\multicolumn{3}{|c|}{Data type \texttt{pairwise5view5} with prestored data} \\ \hline
Long Skip Type 0 Arch.   & 9.65e-01 $\pm$ 5.54e-02 & 1.07e-01 $\pm$ 1.57e-01 \\ \hline
Long Skip Type 0 Arch.   & 9.86e-01 $\pm$ 4.68e-02 & 5.57e-02 $\pm$ 1.38e-01 \\ \hline
Long Skip Type 1 Arch.   & 9.68e-01 $\pm$ 4.40e-02 & 1.20e-01 $\pm$ 1.47e-01 \\ \hline
Long Skip Type 1 Arch.   & 9.90e-01 $\pm$ 2.68e-02 & 5.84e-02 $\pm$ 1.37e-01 \\ \hline
      \end{tabular}
      \label{fig:tab1}
\end{table}

\subsubsection*{Thoughts}
To my dismay, the GAT architecture seems very unstable to train and doesn't converge very well if at all. Comparitavely, the best results come from stacking many layers - on the order of 15 seems to work for these problems pretty well. Now the best thing to do would be to go to real data since these seem to be working pretty well. To get better results we really do need additional losses though.
On the flip side, the Long Skip was a great discovery and works really well, much better than any of the previous architectures. It needs to get more layers for more views... this I am guessing a fundamental limitation. I wonder if there is a way to get around this.
